---
title: "R Notebook"
output: html_notebook
---

4/27/19

Hoping to make up for lost time from last week this week. If I work on R a little bit each day, I should be able to learn quite a bit!

I'm working here in R Markdown/Notebook mode, as I read somewhere it's a good practice to do so.

Today, I'll be working on the 3rd Handout from my STA 100 course. It will be using the built-in dataset *cars*.

QQ-PLOT OR NORMAL PROBABILITY PLOT
```{r}
# QQ-Plot, aka Normal Probability Plot
  #checks normality of data distribution
  #normality = a method to determine outliers, skewness, etc.

class(cars)
View(cars)
#remember: it is a good practice to start by looking at the class of the data, as well as at the data itself.
  #we see that the class is "dataframe."

qqnorm(cars$speed, main = "Normality Plot for Car Speed")
qqline(cars$speed) #<-- gives us the line itself

```


CALCULATING PROPORTIONS OF DATA BETWEEN 1, 2, or 3 STANDARD DEVIATIONS FROM THE MEAN
```{r}
#we will be making and saving info about our data
#our dataset is "cars," and we can look at stuff like sd and mean

X = cars$speed
the_mean = mean(X)
the_sd = sd(X)
within_one_sd = mean(X < the_mean + the_sd & X > the_mean - the_sd)
within_one_sd

#the above is what the worksheet wants me to do, though I wonder if I can get R to print out just *one* of the sd values:
the_mean + the_sd
#okay, that works. Could I get a coordinate of two values, then?
one_sd_away = c(the_mean + the_sd, the_mean - the_sd)
one_sd_away
#cool, so the above code DOES give me two values for SD. so then, what if...
another_way_within_one_sd = mean(X < one_sd_away[1] & X > one_sd_away[2])
another_way_within_one_sd

#in hindsight, I think this process was less efficient in terms of how much I had to type, but it's neat that I figured out that I didn't forget too much in the time I didn't code.

#as the worksheet implies, of course, we can easily calculate how much of our data is within 2 standard dev's
within_two_sd = mean(X < the_mean + 2*the_sd & X > the_mean - 2*the_sd)
within_two_sd


```









